---
title: "UNM06"
output:
  pdf_document: default
date: "2023-09-14"
---

```{r setup, include=FALSE}
library(tidyverse)
library(afex)
library(BayesFactor)
library(apa)
library(emmeans)
library("writexl")
load("UNM06_proc_data.RData")
# function to force scientific formatting of numbers (used for large BFs)
changeSciNot <- function(n) {
  output <- format(n, scientific = TRUE, digits = 2) #Transforms the number into scientific notation even if small
  output <- sub("e", "x10^", output) #Replace e with 10^
  output <- sub("\\+0?", "", output) #Remove + symbol and leading zeros on exponent, if > 1
  output <- sub("-0?", "-", output) #Leaves - symbol but removes leading zeros on exponent, if < 1
  output <- paste0(output,"^")
  # output = strsplit(output, "^", fixed = TRUE)
  # output = paste0(output[[1]][1],"^", output[[1]][2], "^")
  output
}

# function to extract and report BFs with error %s
report_BF_and_error <- function(BF_in, sci_not = TRUE, hyp = "alt"){
  
  if (hyp == "alt") {
    BF_notation = "BF~10~ = "
  } else if (hyp == "null") {
    BF_notation = "BF~01~ = "
  }
  
  if (sci_not == TRUE) {
    BF_value = changeSciNot(extractBF(BF_in)$bf) # change to sci notation
  } else {
    BF_value = round(extractBF(BF_in)$bf,2) # otherwise round
  }
  
  paste0(BF_notation, 
         BF_value, 
         " &plusmn; ", 
         round(100*extractBF(BF_in)$error,2), 
         "%")
}

```

# Design

In this experiment, the differences in recognition memory of predictive and non-predictive cues was examined under both a certain and an uncertain training. Both groups received a training in which two cues are presented in each trial followed by an outcome. Only one of the cues is predictive of the outcome, whereas the other appears the same amount of times with each of the two possible outcomes. In one of this groups, the contingency between the predictive cues and their respective outcomes is of 1, so in each trial that the predictive cue is presented its corresponding outcome follows. For the other group, this contingency is of 0.8, so the predictive cue is followed by the outcome on 80% of the trials. After the training phase, all subjects were presented two cues on each trial, one that was presented on training and one that wasn't, but that was similar to the other cues presented on the training phase (a pair of balls swapped colours in the fouls). Subjects had to choose which one they had seen before and rate how confident they were of their choice.

+------------+---------------------------+------------+
| Group      | Training                  | Test2      |
+============+:=========================:+:==========:+
| Certain    | AX - O1                   | A vs *b*   |
|            |                           |            |
|            |                           | A vs *x*   |
|            |                           |            |
|            |                           | A vs *y*   |
+------------+---------------------------+------------+
|            | AY - O1                   | B vs *a*   |
|            |                           |            |
|            |                           | B vs *x*   |
|            |                           |            |
|            |                           | B vs *y*   |
+------------+---------------------------+------------+
|            | BX - 02                   | X vs *a*   |
|            |                           |            |
|            |                           | X vs *b*   |
|            |                           |            |
|            |                           | X vs *y*   |
+------------+---------------------------+------------+
|            | BY - O2                   | Y vs *a*   |
|            |                           |            |
|            |                           | Y vs *b*   |
|            |                           |            |
|            |                           | Y vs *x*   |
+------------+---------------------------+------------+
| Uncertain  | 0.8 AX - O1 / 0.2 AX - O2 | A vs *b*   |
|            |                           |            |
|            |                           | A vs *x*   |
|            |                           |            |
|            |                           | A vs *y*   |
+------------+---------------------------+------------+
|            | 0.8 AY - O1 / 0.2 AY - O2 | B vs *a*   |
|            |                           |            |
|            |                           | B vs *x*   |
|            |                           |            |
|            |                           | B vs *y*   |
+------------+---------------------------+------------+
|            | 0.8 BX - O1 / 0.2 BX - O2 | X vs *a*   |
|            |                           |            |
|            |                           | X vs *b*   |
|            |                           |            |
|            |                           | X vs *y*   |
+------------+---------------------------+------------+
|            | 0.8 BY - O1 / 0.2 BY - O2 | Y vs *a*   |
|            |                           |            |
|            |                           | Y vs *b*   |
|            |                           |            |
|            |                           | Y vs *x*   |
+------------+---------------------------+------------+

# Results
## Test
### Accuracy
```{r, include = FALSE}
test <- test %>%
  mutate(trial_type = case_when((target == 1 & distractor == 2) | (target == 2 & distractor == 1) ~ "RP",
                                (target == 5 & distractor == 6) | (target == 6 & distractor == 5) ~ "RNP",
                                (target == 1 & (distractor == 5 | distractor == 6)) | (target == 2 & (distractor == 5 | distractor == 6)) ~ "FP",
                                (target == 5 & (distractor == 1 | distractor == 2)) | (target == 6 & (distractor == 1 | distractor == 2)) ~ "FNP",
                                (target == 3 & distractor == 4) | (target == 4 & distractor == 3) ~ "RP",
                                (target == 7 & distractor == 8) | (target == 8 & distractor == 7) ~ "RNP",
                                (target == 3 & (distractor == 7 | distractor == 8)) | (target == 4 & (distractor == 7 | distractor == 8)) ~ "FP",
                                (target == 7 & (distractor == 3 | distractor == 4)) | (target == 8 & (distractor == 3 | distractor == 4)) ~ "FNP"),
         cue_trial_type = case_when(trial_type == "RP" & condition == "Uncertain" ~ "U_RP",
                                    trial_type == "RP" & condition == "Certain" ~ "C_RP",
                                    trial_type == "RNP" & condition == "Uncertain" ~ "U_RNP",
                                    trial_type == "RNP" & condition == "Certain" ~ "C_RNP",
                                    trial_type == "FP" & condition == "Uncertain" ~ "U_FP",
                                    trial_type == "FP" & condition == "Certain" ~ "C_FP",
                                    trial_type == "FNP" & condition == "Uncertain" ~ "U_FNP",
                                    trial_type == "FNP" & condition == "Certain" ~ "C_FNP"),
         predictiveness = case_when(trial_type == "RP" ~ "predictive",
                                    trial_type == "RNP"  ~ "non-predictive",
                                    trial_type == "FP" ~ "predictive",
                                    trial_type == "FNP" ~ "non-predictive"),
         congruence = case_when(trial_type == "RP" ~ "congruent",
                                    trial_type == "RNP"  ~ "congruent",
                                    trial_type == "FP" ~ "incongruent",
                                    trial_type == "FNP" ~ "incongruent"))

MA_test <- test %>%
  group_by(cue_trial_type, condition) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE),
            sd_acc = sd(acc, na.rm = TRUE)/sqrt(length(acc)))
```
```{r, echo = FALSE}
ggplot(MA_test) +
  geom_col(mapping = aes(x = cue_trial_type, y = mean_acc, fill = condition)) +
  geom_errorbar(aes(x= cue_trial_type, y = mean_acc, ymin = mean_acc-sd_acc, ymax = mean_acc+sd_acc), color = "black", width=.1,position=position_dodge(0.05)) +
  labs(title = "Mean accuracy in the test phase")
```
```{r, include=FALSE}
#ANOVA
acc_test <- test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_acc = mean(acc, na.rm = TRUE))
acc_test$pNum <- factor(acc_test$pNum)
acc_test$condition <- factor(acc_test$condition)
acc_test$predictiveness <- factor(acc_test$predictiveness)
acc_test$congruence <- factor(acc_test$congruence)
ANOVA_acc_test <- aov_car(formula = mean_acc ~ condition + Error(pNum/predictiveness*congruence), data = acc_test)
print(ANOVA_acc_test)
bay_ANOVA_acc_test <- anovaBF(formula = mean_acc ~ condition + predictiveness + congruence + pNum,
        data = data.frame(acc_test),
        whichRandom = "pNum")
print(bay_ANOVA_acc_test)
bay_ANOVA_acc_test_condxp <- bay_ANOVA_acc_test[4]/bay_ANOVA_acc_test[3]
print(bay_ANOVA_acc_test_condxp)
bay_ANOVA_acc_test_pxcong <- bay_ANOVA_acc_test[13]/bay_ANOVA_acc_test[7]
print(bay_ANOVA_acc_test_pxcong)
bay_ANOVA_acc_test_condxcong <- bay_ANOVA_acc_test[10]/bay_ANOVA_acc_test[6]
print(bay_ANOVA_acc_test_condxcong)
bay_ANOVA_acc_test_condxpxcong <- bay_ANOVA_acc_test[18]/bay_ANOVA_acc_test[17]
print(bay_ANOVA_acc_test_condxpxcong)
```
There are no differences in accuracy due to the condition, the predictiveness, the congruence or any of the interactions of them (Condition: `r apa(ANOVA_acc_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_acc_test[1])`; Predictiveness: `r apa(ANOVA_acc_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test[2])`; Congruence: `r apa(ANOVA_acc_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test[5])`  ; ConditionxPredictiveness: `r apa(ANOVA_acc_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_test_condxp[1])`); PredictivenessxCongruence: `r apa(ANOVA_acc_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_pxcong[1])`; ConditionxCongruence: `r apa(ANOVA_acc_test, effect = "condition:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_condxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_acc_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_test_condxpxcong[1])`). All bayesian effects were mdoerate null, except for the main effecto of the condition, that was anecdotal null.

### Memory score
```{r, include = FALSE}
MM_test <- test %>%
  group_by(cue_trial_type, condition) %>%
  summarise(mean_mem = mean(mem_score, na.rm = TRUE),
            sd_mem = sd(mem_score, na.rm = TRUE)/sqrt(length(mem_score)))
```
```{r, echo = FALSE}
ggplot(MM_test) +
  geom_col(mapping = aes(x = cue_trial_type, y = mean_mem, fill = condition)) +
  geom_errorbar(aes(x= cue_trial_type, y = mean_mem, ymin = mean_mem-sd_mem, ymax = mean_mem+sd_mem), color = "black", width=.1,position=position_dodge(0.05)) +
  labs(title = "Mean memory score in the test phase")
```
```{r, include=FALSE}
#ANOVA
mem_test <- test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_mem = mean(mem_score, na.rm = TRUE))
mem_test$pNum <- factor(mem_test$pNum)
mem_test$condition <- factor(mem_test$condition)
mem_test$predictiveness <- factor(mem_test$predictiveness)
mem_test$congruence <- factor(mem_test$congruence)
ANOVA_mem_test <- aov_car(formula = mean_mem ~ condition + Error(pNum/predictiveness*congruence), data = mem_test)
print(ANOVA_mem_test)
bay_ANOVA_mem_test <- anovaBF(formula = mean_mem ~ condition + predictiveness + congruence + pNum,
        data = data.frame(mem_test),
        whichRandom = "pNum")
print(bay_ANOVA_mem_test)
bay_ANOVA_mem_test_condxp <- bay_ANOVA_mem_test[4]/bay_ANOVA_mem_test[3]
print(bay_ANOVA_mem_test_condxp)
bay_ANOVA_mem_test_pxcong <- bay_ANOVA_mem_test[13]/bay_ANOVA_mem_test[7]
print(bay_ANOVA_mem_test_pxcong)
bay_ANOVA_mem_test_condxcong <- bay_ANOVA_mem_test[10]/bay_ANOVA_mem_test[6]
print(bay_ANOVA_mem_test_condxcong)
bay_ANOVA_mem_test_condxpxcong <- bay_ANOVA_mem_test[18]/bay_ANOVA_mem_test[17]
print(bay_ANOVA_mem_test_condxpxcong)
```
There are no differences in accuracy due to the condition, the predictiveness, the congruence or any of the interactions of them (Condition: `r apa(ANOVA_mem_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_mem_test[1])`; Predictiveness: `r apa(ANOVA_mem_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_test[2])`; Congruence: `r apa(ANOVA_mem_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test[5])`  ; ConditionxPredictiveness: `r apa(ANOVA_mem_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_test_condxp[1])`); PredictivenessxCongruence: `r apa(ANOVA_mem_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_pxcong[1])`; ConditionxCongruence: `r apa(ANOVA_mem_test, effect = "condition:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_condxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_mem_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_test_condxpxcong[1])`). All bayesian effects were anecdotal null, except for the main effects of the Predictiveness, Congruence and the ConditionxCongruence interaction, that was moderate.

### Corrected memory score (hits x1, errors x0)
```{r, include = FALSE}
Mc_mem_test <- test %>%
  group_by(cue_trial_type, condition) %>%
  summarise(mean_c_mem = mean(c_mem_score, na.rm = TRUE),
            sd_c_mem = sd(c_mem_score, na.rm = TRUE)/sqrt(length(c_mem_score)))
```
```{r, echo = FALSE}
ggplot(Mc_mem_test) +
  geom_col(mapping = aes(x = cue_trial_type, y = mean_c_mem, fill = condition)) +
  geom_errorbar(aes(x= cue_trial_type, y = mean_c_mem, ymin = mean_c_mem-sd_c_mem, ymax = mean_c_mem+sd_c_mem), color = "black", width=.1,position=position_dodge(0.05)) +
  labs(title = "Mean corrected memory score in the test phase")
```
```{r, include=FALSE}
#ANOVA
c_mem_test <- test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_c_mem = mean(c_mem_score, na.rm = TRUE))
c_mem_test$pNum <- factor(c_mem_test$pNum)
c_mem_test$condition <- factor(c_mem_test$condition)
c_mem_test$predictiveness <- factor(c_mem_test$predictiveness)
c_mem_test$congruence <- factor(c_mem_test$congruence)
ANOVA_c_mem_test <- aov_car(formula = mean_c_mem ~ condition + Error(pNum/predictiveness*congruence), data = c_mem_test)
print(ANOVA_c_mem_test)

bay_ANOVA_c_mem_test <- anovaBF(formula = mean_c_mem ~ condition + predictiveness +congruence + pNum,
        data = data.frame(c_mem_test),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_test)
bay_ANOVA_c_mem_test_condxp <- bay_ANOVA_c_mem_test[4]/bay_ANOVA_c_mem_test[3]
print(bay_ANOVA_c_mem_test_condxp)
bay_ANOVA_c_mem_test_pxcong <- bay_ANOVA_c_mem_test[13]/bay_ANOVA_c_mem_test[7]
print(bay_ANOVA_c_mem_test_pxcong)
bay_ANOVA_c_mem_test_condxcong <- bay_ANOVA_c_mem_test[10]/bay_ANOVA_c_mem_test[6]
print(bay_ANOVA_c_mem_test_condxcong)
bay_ANOVA_c_mem_test_condxpxcong <- bay_ANOVA_c_mem_test[18]/bay_ANOVA_c_mem_test[17]
print(bay_ANOVA_c_mem_test_condxpxcong)
```
There are no differences in accuracy due to the condition, the predictiveness, the congruence or any of the interactions of them (Condition: `r apa(ANOVA_c_mem_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[1])`; Predictiveness: `r apa(ANOVA_c_mem_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[2])`; Congruence: `r apa(ANOVA_c_mem_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test[5])`  ; ConditionxPredictiveness: `r apa(ANOVA_c_mem_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_condxp[1])`); PredictivenessxCongruence: `r apa(ANOVA_c_mem_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_pxcong[1])`; ConditionxCongruence: `r apa(ANOVA_c_mem_test, effect = "condition:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_condxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_c_mem_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_test_condxpxcong[1])`). All Bayesian effects were moderate null, except for the  ConditionxPredictiveness interaction, that was anecdotal.

### Corrected memory score (with errors out)
```{r, include = FALSE}
c_test <- filter(test, acc == 1)
MCMS_test <- c_test %>%
  group_by(cue_trial_type, condition) %>%
  summarise(mean_mem = mean(mem_score, na.rm = TRUE),
            sd_mem = sd(mem_score, na.rm = TRUE)/sqrt(length(mem_score)))
```
```{r, echo = FALSE}
ggplot(MCMS_test) +
  geom_col(mapping = aes(x = cue_trial_type, y = mean_mem, fill = condition)) +
  geom_errorbar(aes(x= cue_trial_type, y = mean_mem, ymin = mean_mem-sd_mem, ymax = mean_mem+sd_mem), color = "black", width=.1,position=position_dodge(0.05)) +
  labs(title = "Mean corrected memory score in the test phase")
```
```{r, include=FALSE}
#ANOVA
cms_test <- c_test %>%
  group_by (pNum, condition, predictiveness, congruence) %>%
  summarise(mean_mem = mean(mem_score, na.rm = TRUE))
cms_test$pNum <- factor(cms_test$pNum)
cms_test$condition <- factor(cms_test$condition)
cms_test$predictiveness <- factor(cms_test$predictiveness)
cms_test$congruence <- factor(cms_test$congruence)
ANOVA_cms_test <- aov_car(formula = mean_mem ~ condition + Error(pNum/predictiveness*congruence), data = cms_test)
print(ANOVA_cms_test)

bay_ANOVA_cms_test <- anovaBF(formula = mean_mem ~ condition + predictiveness + congruence + pNum,
        data = data.frame(cms_test),
        whichRandom = "pNum")
print(bay_ANOVA_cms_test)

bay_ANOVA_cms_test_condxp <- bay_ANOVA_cms_test[4]/bay_ANOVA_cms_test[3]
print(bay_ANOVA_cms_test_condxp)
bay_ANOVA_cms_test_pxcong <- bay_ANOVA_cms_test[13]/bay_ANOVA_cms_test[7]
print(bay_ANOVA_cms_test_pxcong)
bay_ANOVA_cms_test_condxcong <- bay_ANOVA_cms_test[10]/bay_ANOVA_cms_test[6]
print(bay_ANOVA_cms_test_condxcong)
bay_ANOVA_cms_test_condxpxcong <- bay_ANOVA_cms_test[18]/bay_ANOVA_cms_test[17]
print(bay_ANOVA_cms_test_condxpxcong)
```
There are no differences in accuracy due to the condition, the predictiveness, the congruence or any of the interactions of them (Condition: `r apa(ANOVA_cms_test, effect = "condition")`, `r report_BF_and_error(bay_ANOVA_cms_test[1])`; Predictiveness: `r apa(ANOVA_cms_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_cms_test[2])`; Congruence: `r apa(ANOVA_cms_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_cms_test[5])`  ; ConditionxPredictiveness: `r apa(ANOVA_cms_test, effect = "condition:predictiveness")`, `r report_BF_and_error(bay_ANOVA_cms_test_condxp[1])`); PredictivenessxCongruence: `r apa(ANOVA_cms_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_cms_test_pxcong[1])`; ConditionxCongruence: `r apa(ANOVA_cms_test, effect = "condition:congruence")`, `r report_BF_and_error(bay_ANOVA_cms_test_condxcong[1])`; ConditionxPredictivenessxCongruence: `r apa(ANOVA_cms_test, effect = "condition:predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_cms_test_condxpxcong[1])`). All Bayesian effects were anecdotal null, except for the Condition main effect, and the ConditionxCongruence and ConditionxPredictivenessxCongruence interactions. These interactions showed anecdotal null interaction. However, is worth noting that the effect of condition was marginally significant, and with anecdotal Bayesian evidence for the alternative hypothesis.


## Certain only results
```{r, include = FALSE}
cert_test <- filter(test, condition == "Certain")
```

### Accuracy
```{r, include=FALSE}
#t test accuracy
acc_cert_test <- cert_test %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(acc = mean(acc, na.rm = TRUE))
acc_cert_test$pNum <- factor(acc_cert_test$pNum)
acc_cert_test$predictiveness <- factor(acc_cert_test$predictiveness)
acc_cert_test$congruence <- factor(acc_cert_test$congruence)
ANOVA_acc_cert_test <- aov_car(formula = acc ~ Error(pNum/predictiveness*congruence), data = acc_cert_test)
print(ANOVA_acc_cert_test)

bay_ANOVA_acc_cert_test <- anovaBF(formula = acc ~ predictiveness + congruence + pNum,
        data = data.frame(acc_cert_test),
        whichRandom = "pNum")
print(bay_ANOVA_acc_cert_test)
bay_ANOVA_acc_cert_test_int <- bay_ANOVA_acc_cert_test[4]/bay_ANOVA_acc_cert_test[3]
print(bay_ANOVA_acc_cert_test_int)
```
There are no differences in accuracy due to predictiveness, congruence or the interaction, and the bayesian analysis indicates moderate evidence for the null hypothesis in all cases (Predictiveness: `r apa(ANOVA_acc_cert_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_acc_cert_test[1])`; Congruence: `r apa(ANOVA_acc_cert_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_acc_cert_test[2])`; PredictivenessxCongruence: `r apa(ANOVA_acc_cert_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_acc_cert_test_int[1])`.

### Memory score

```{r, include=FALSE}
#ANOVA
mem_cert_test <- cert_test %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem = mean(mem_score, na.rm = TRUE))
mem_cert_test$pNum <- factor(mem_cert_test$pNum)
mem_cert_test$predictiveness <- factor(mem_cert_test$predictiveness)
mem_cert_test$congruence <- factor(mem_cert_test$congruence)
ANOVA_mem_cert_test <- aov_car(formula = mem ~ Error(pNum/predictiveness*congruence), data = mem_cert_test)
print(ANOVA_mem_cert_test)

bay_ANOVA_mem_cert_test <- anovaBF(formula = mem ~ predictiveness + congruence + pNum,
        data = data.frame(mem_cert_test),
        whichRandom = "pNum")
print(bay_ANOVA_mem_cert_test)
bay_ANOVA_mem_cert_test_int <- bay_ANOVA_mem_cert_test[4]/bay_ANOVA_mem_cert_test[3]
print(bay_ANOVA_mem_cert_test_int)
```
There are no differences in memory score due to predictiveness, congruence or the interaction, and the bayesian analysis indicates moderate evidence for the null hypothesis in all cases (Predictiveness: `r apa(ANOVA_mem_cert_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_mem_cert_test[1])`; Congruence: `r apa(ANOVA_mem_cert_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_mem_cert_test[2])`; PredictivenessxCongruence: `r apa(ANOVA_mem_cert_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_mem_cert_test_int[1])`.

### Corrected memory score (hits x1, errors x0)
```{r, include=FALSE}
c_mem_cert_test <- cert_test %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(c_mem = mean(c_mem_score, na.rm = TRUE))
c_mem_cert_test$pNum <- factor(c_mem_cert_test$pNum)
c_mem_cert_test$predictiveness <- factor(c_mem_cert_test$predictiveness)
c_mem_cert_test$congruence <- factor(c_mem_cert_test$congruence)
ANOVA_c_mem_cert_test <- aov_car(formula = c_mem ~ Error(pNum/predictiveness*congruence), data = c_mem_cert_test)
print(ANOVA_c_mem_cert_test)

bay_ANOVA_c_mem_cert_test <- anovaBF(formula = c_mem ~ predictiveness + congruence + pNum,
        data = data.frame(c_mem_cert_test),
        whichRandom = "pNum")
print(bay_ANOVA_c_mem_cert_test)
bay_ANOVA_c_mem_cert_test_int <- bay_ANOVA_c_mem_cert_test[4]/bay_ANOVA_c_mem_cert_test[3]
print(bay_ANOVA_c_mem_cert_test_int)
```
There are no differences in memory score due to predictiveness, congruence or the interaction, and the bayesian analysis indicates moderate evidence for the null hypothesis in all cases (Predictiveness: `r apa(ANOVA_c_mem_cert_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_mem_cert_test[1])`; Congruence: `r apa(ANOVA_c_mem_cert_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_cert_test[2])`; PredictivenessxCongruence: `r apa(ANOVA_c_mem_cert_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_mem_cert_test_int[1])`.

### Corrected memory score (with errors out)
```{r, include = FALSE}
c_cert_test <- filter(cert_test, acc == 1)
cms_cert_test <- c_cert_test %>%
  group_by (pNum, predictiveness, congruence) %>%
  summarise(mem = mean(mem_score, na.rm = TRUE))
cms_cert_test$pNum <- factor(cms_cert_test$pNum)
cms_cert_test$predictiveness <- factor(cms_cert_test$predictiveness)
cms_cert_test$congruence <- factor(cms_cert_test$congruence)
ANOVA_cms_cert_test <- aov_car(formula = mem ~ Error(pNum/predictiveness*congruence), data = cms_cert_test)
print(ANOVA_cms_cert_test)

bay_ANOVA_cms_cert_test <- anovaBF(formula = mem ~ predictiveness + congruence + pNum,
        data = data.frame(cms_cert_test),
        whichRandom = "pNum")
print(bay_ANOVA_cms_cert_test)
bay_ANOVA_cms_cert_test_int <- bay_ANOVA_cms_cert_test[4]/bay_ANOVA_cms_cert_test[3]
print(bay_ANOVA_cms_cert_test_int)
```
There are no differences in memory score due to predictiveness, congruence or the interaction, and the bayesian analysis indicates anecdotal evidence for the null hypothesis of the predictiveness and moderate for the congruence and the interaction (Predictiveness: `r apa(ANOVA_c_cert_test, effect = "predictiveness")`, `r report_BF_and_error(bay_ANOVA_c_cert_test[1])`; Congruence: `r apa(ANOVA_c_cert_test, effect = "congruence")`, `r report_BF_and_error(bay_ANOVA_c_cert_test[2])`; PredictivenessxCongruence: `r apa(ANOVA_c_cert_test, effect = "predictiveness:congruence")`, `r report_BF_and_error(bay_ANOVA_c_cert_test_int[1])`.